ICS Phenotyping

### 2019-06-17 ICS_Phenotyping.Rmd
narrowed down to LTBI and TB. Includes mtb to total comps

@@

#Comparing Mtb-Specific to Total
```{r}
total<-read.csv("/Applications/Old Computer/Day Lab/Flow-Data/Clean/ICS_CD4_clean.csv")
total$cell<-"Total"
names<-c("Donor", "TB", "SM", "Stim", names(phenotype)[grep("TH1_", names(phenotype))])
mtb_th1<-select(phenotype, names)
names(mtb_th1)<-gsub("TH1_", "", names(mtb_th1))
mtb_th1$cell<-"Mtb-Specific"
test<-rbindlist(list(total, mtb_th1), fill=TRUE)
    test<-filter(test, SM!="N", TB!="HC") 
    test$SM<-factor(test$SM, levels=c("X","SM"))
    test$TB<-factor(test$TB, levels=c("LTBI","TB"))
test2<-merge(total, mtb_th1, by=c("Donor","TB","SM","Stim"))
    test2<-filter(test2, SM!="N", TB!="HC") 
    test2$SM<-factor(test2$SM, levels=c("X","SM"))
    test2$TB<-factor(test2$TB, levels=c("LTBI","TB"))
```

@@

>>>>

```{r}
test<-mutate_TB(filter(DF, !is.na(TH1_GATA3)))
kable(xtabs(~TB+SM, test))
plot_2(test, "disease", "TH1_GATA3")
plot_2(test, "disease", "TH1_t_x_x_4")
plot_2(test, "disease", "TH1_t_x_x_x")
plot_2(test, "disease", "TH1_x_g_3_4")
plot_2(test, "disease", "TH1_x_g_3_x")
plot_2(test, "disease", "TH1_x_g_x_4")
plot_2(test, "disease", "TH1_x_x_3_x")

grid.arrange(plot_2(test, "disease", "TH1_t_x_x_x")+labs(y="Tbet+ CD4+ T cells"),
plot_2(test, "disease", "TH1_t_x_x_4")+labs(y="CCR4+Tbet+ CD4+ T Cells (%)"),
    plot_2(test, "disease", "TH1_GATA3")+labs(y="GATA3+ CD4+ T cells (%)"),
ncol=3
)
```

@@

#Comparing Mtb-Specific to Total
This is only within TH1 cells
```{r}
total<-read.csv("/Applications/Old Computer/Day Lab/Flow-Data/Clean/ICS_CD4_clean.csv")
total$cell<-"Total"
names<-c("Donor", "TB", "SM", "Stim", names(phenotype)[grep("TH1_", names(phenotype))])
mtb_th1<-select(phenotype, names)
names(mtb_th1)<-gsub("TH1_", "", names(mtb_th1))
mtb_th1$cell<-"Mtb-Specific"
test<-rbindlist(list(total, mtb_th1), fill=TRUE)
    test<-filter(test, SM!="N", TB!="HC") 
    test$SM<-factor(test$SM, levels=c("X","SM"))
    test$TB<-factor(test$TB, levels=c("LTBI","TB"))
test2<-merge(total, mtb_th1, by=c("Donor","TB","SM","Stim"))
    test2<-filter(test2, SM!="N", TB!="HC") 
    test2$SM<-factor(test2$SM, levels=c("X","SM"))
    test2$TB<-factor(test2$TB, levels=c("LTBI","TB"))
```

@@

```{r}
t<-mutate_TB(filter(df1, !is.na(GATA3)))
t$cell<-factor(t$cell, levels=c("Total", "Mtb-Specific"))
plot_compare(t, "cell", "GATA3")
plot_compare(t, "cell", "t_x_x_4")
plot_compare(t, "cell", "t_x_x_x")
plot_compare(t, "cell", "x_g_3_4")
plot_compare(t, "cell", "x_g_3_x")
plot_compare(t, "cell", "x_g_x_4")
plot_compare(t, "cell", "x_x_3_x")
```
